Evaluating the Supportive Effect of Feature Selection Methods on Machine Learning Models in Monitoring Forest Health Using Hyperspectral Remote Sensing Data

### 2020-04-05 docs/00-manuscripts/ieee/ieee-manuscript.tex
AB-review: optimize VI vs NRI intro

Vegetation indices have shown the potential to provide valuable information when analyzing forest health \cite{jiang2014, adamczyk2015}.
Most vegetation indices were developed with the aim of being sensitive to changes of specific wavelength regions, serving as a proxy for underlying plant processes. 
However, often enough indices developed for different purposes than the one to be analyzed can help to explain complex relationships.
This emphasizes the need to extract as much information as possible from the available input data to generate promising features which can help to understand the modeled relationship.
A less known index type which can be derived from spectral information is called normalized ratio index (NRI).
In contrast to \ac{VI}, \ac{NRI}s are not based on an expert-based formulas following environmental heuristics but use a data-driven feature engineering approach by combining (arbitrary) combinations of spectral bands.
Especially when working with hyperspectral data, hundreds of \ac{NRI} features can be derived this way.

>>>>

Vegetation indices have shown the potential to provide valuable information when analyzing forest health \cite{jiang2014, adamczyk2015}.
Most vegetation indices were developed with the aim of being sensitive to changes of specific wavelength regions, serving as a proxy for underlying plant processes. 
However, often enough indices developed for different purposes than the one to be analyzed can help to explain complex relationships.
This emphasizes the need to extract as much information as possible from the available input data to generate promising features which can help to understand the modeled relationship.
A less known index type which can be derived from spectral information is the normalized ratio index (NRI).
In contrast to most \ac{VI} indices, the \ac{NRI} does not use an expert-based formula following environmental heuristics but instead makes use of a data-driven feature engineering approach by combining (arbitrary) combinations of spectral bands.
Especially when working with hyperspectral data, thousands of \ac{NRI} features can be derived this way.
